---
title: "p8105_hw1_yw4251"
author: "You Wu"
date: 2023-09-17
output: github_document
---

First, we load package and load `early_january_weather` dataset.
```{r}
library(moderndive)
data("early_january_weather")
early_january_weather
```
```{r,eval=FALSE}
help(early_january_weather)
```

# Early January hourly weather data

**Description**

Hourly meterological data for LGA, JFK and EWR for the month of January 2013. This is a subset of the weather data frame from nycflights13. A data frame of `r nrow(early_january_weather)` rows representing hourly measurements and `r ncol(early_january_weather)` variables.

**Variables**

**_origin:_** Weather station. Named `origin` to facilitate merging with nycflights13::flights data.

**_year, month, day, hour:_** Time of recording.

**_temp, dewp:_** Temperature and dewpoint in F.

**_humid:_** Relative humidity.

**_wind_dir, wind_speed, wind_gust:_** Wind direction (in degrees), speed and gust speed (in mph).

**_precip:_** Precipitation, in inches.

**_pressure:_** Sea level pressure in millibars.

**_visib:_** Visibility in miles.

**_time_hour:_** Date and hour of the recording as a POSIXct date.

I could calculate the mean of temperature.
The mean is `r round(mean(early_january_weather$temp),digits=4)` F.
